### 2025-05-07 chapters/1-qcd.tex
Adjusted timeline text

\begin{figure}[]
    {
        \hspace{-1.7cm}
        \input{includes/timeline.tikz}
    }
    \caption[A rough timeline of the history of \gls{qcd}. \sam{incomplete}]
    {
        A rough timeline of the history of \gls{qcd}.
        %
        \sam{Not complete! Many particles, as well as QGP, missing! May want to change notation, e.g. for particle discoveries}
        %
        \sam{Noah recommends lines connecting things to dates...}
    }
    \label{fig:qcd-timeline}
\end{figure}

>>>>

\begin{figure}[]
    {
        \hspace{-2.8cm}
        \input{includes/timeline.tikz}
    }
    \caption[A rough timeline of the history of \gls{qcd}.]
    {
        A rough timeline of the history of \gls{qcd}.
    }
    \label{fig:qcd-timeline}
\end{figure}
